Investigating motor vehicle collisions in Toronto: Installing more red light cameras do not stop traffic accidents from happening

### 2022-02-07 outputs/paper/paper.Rmd
finalize

# Discussion
The analysis of the two datasets show no relationship between the cases of motor vehicle collisions in Toronto and the number of red light cameras. From the comparison between Figure 3 and Figure 4, we see that in none of the districts did the number of vehicle collisions followed the trend of the installations of the red light cameras. For stance, between 2016 and 2017, all four districts made the installations of lots of new red light cameras, but none of the data in Figure 4 seemed to reflect that action. The implication of Section \@ref(data) is that: installing more red cameras does not change the number of traffic accidents in Toronto, nor does it influence the fatality of the accidents. A very likely reason to explain this situation is that red light cameras only concerned the drivers who already followed the rule most of the time, but not the rule-breaking drivers. Another possible reason would be that at intersections with red light cameras, more drivers would intend to stop rather than to proceed when they see the light is about to turn red, resulting in a higher chance of rear end accidents [@cite2].

In recent years, complaints have been raised about whether red light cameras are used mainly to prevent injuries and deaths from traffic accidents or earn revenues for the government [@cite3]. Measures should be taken to improve the effectiveness of this system and to ensure the safety of drivers and pedestrians who are the victims of the vehicle accidents. For instance, drivers should be more notified on the existence of red light cameras, instead of knowing them after they are fined, because red light cameras is supposed to prevent accidents but not to punish people after they cause accidents. Government could also seek for other solutions to reduce these accidents. Toronto and East York has done a great job reducing the number of motor vehicle collisions, which means that other district could adopt similar traffic controls and see how it works in a few years.

>>>>

# Discussion
The analysis of the two datasets shows no relationship between the cases of motor vehicle collisions in Toronto and the number of red light cameras. From the comparison between Figure 3 and Figure 4, we see that in none of the districts did the number of vehicle collisions followed the trend of the installations of the red light cameras. For instance, between 2016 and 2017, all four districts made the installations of lots of new red light cameras, but none of the bar plot in Figure 4 seemed to reflect that action. The implication of Section \@ref(data) is that: installing more red cameras does not change the number of traffic accidents in Toronto, nor does it influence the fatality of the accidents. A very likely reason to explain this situation is that red light cameras only concerned the drivers who already followed the rule most of the time, but not the rule-breaking drivers. Another possible reason would be that at intersections with red light cameras, more drivers would intend to stop rather than to proceed when they see the light is about to turn red, resulting in a higher chance of rear end accidents [@cite2].

In recent years, complaints have been raised about whether red light cameras are used mainly to prevent injuries and deaths from traffic accidents or earn revenues for the government [@cite3]. Measures should be taken to improve the effectiveness of this system and to ensure the safety of the drivers and pedestrians who are victims of the vehicle accidents. For instance, drivers should be more notified on the existence of red light cameras instead of knowing that after they are fined, because red light cameras are supposed to prevent severe accidents from happening but not to punish people after they cause the accidents. Government could also seek for other solutions to reduce those vehicle collisions. Toronto and East York has done a great job reducing the number of traffic collisions from 2006 to 2020, which means that other district could adopt similar traffic controls and see how it works in a few years.
